---
title: "Analyzing 1000 Older Article Revisions"
author: "Kevin"
date: "March 29, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)

library(scales)
library(zoo)

```

load in the data and convert to a data frame
```{r}
revisions <- read.table(file = "data/articlesthatareoldenough.txt", sep = ",", quote = "\"'", stringsAsFactors = FALSE, header = FALSE, strip.white = TRUE)
remove.list <- list('\\[', '\\]')
revisions <- lapply(revisions, gsub, pattern = paste(unlist(remove.list), collapse = "|") , replacement = '')
revisions <- as.data.frame(revisions, stringsAsFactors = FALSE)

revisions_processed <- 
  setNames(
    as.data.frame(lapply(1:ncol(revisions), function (i) {
      type.convert(revisions[,i], as.is = TRUE)
    }), stringsAsFactors = FALSE),
    c("article_id", "article_title", "timestamp", "TEXTDATA")
  )
library(tidyr)
revisions_processed <- separate(data = revisions_processed, col = timestamp, into = c('date', 'time'), sep = "T")
str(revisions_processed)
head(revisions_processed)

article.ids <- unique(revisions_processed$article_id)
# save these to a file for the webscraper
write(article.ids, file = "data/1000articleids.txt")
```

## Date work
Separate the date, create monthly counts
```{r}
date_split <- separate(data = revisions_processed, col = date, into = c('year', 'month', 'day'), sep = "-")
monthlycounts <- date_split %>%
  group_by(article_id, year, month) %>%
  dplyr::summarise(count = n())
arrange(monthlycounts, article_id, year, month)
```
```{r}
revisions_to_dates <- revisions_processed
revisions_to_dates$date <- as.Date(revisions_to_dates$date, '%Y-%m-%d')
str(revisions_to_dates)
```

```{r}
revisions_to_dates$date <- format(revisions_to_dates$date, format="%Y-%m")
revisions_to_dates

collapsed <- revisions_to_dates %>%
  group_by(article_id, date) %>%
  dplyr::summarise(count = n())
arrange(collapsed, desc(count))

library(zoo)
library(scales)
article.revisions.by.year.date <- ggplot(data = collapsed, aes(x=as.yearmon(date), y = count, colour = article_id)) + 
  geom_line(aes(group = article_id)) + 
  geom_point(size = 1.3) + 
  scale_color_gradient2(midpoint = 7000000, labels=comma) + 
  labs(title = "Number of Revisions for Each Article by Month from 2001 to 2008", colour = "Article ID") + 
  xlab("Year-Month") + 
  ylab("Number of Revisions") +
  theme(plot.title = element_text(size = rel(1.3)), axis.ticks.length = unit(.25, "cm"))

#article.revisions.by.year.date

ggsave("img/article-revisions-by-year-date.png", article.revisions.by.year.date, width = 10, height = 6)
```

It could be interesting to look at which articles have such high amounts of revisions.
```{r}
highrevisions <- collapsed %>%
  filter(count > 250)
(highrevisionarticles <- unique(highrevisions$article_id))

ggplot(data = collapsed[which(collapsed$article_id %in% highrevisionarticles),], aes(x=as.yearmon(date), y = count, colour = article_id)) + geom_line(aes(group = article_id)) + geom_point(size = 1.3)

ggsave('img-older/article-revisions-by-month-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)

```
let's normalize by total number of revisions to get percentages to see which ones had most of these edits within a small timespan
```{r}
percents.of.high.revisions <- collapsed[which(collapsed$article_id %in% highrevisionarticles),] %>%
  group_by(article_id) %>%
  mutate(percent = count/sum(count), total = sum(count))

library(zoo)
ggplot(data = percents.of.high.revisions, aes(x=as.yearmon(date), y = percent, colour = total)) + geom_line(aes(group = article_id)) + geom_point() + scale_y_continuous(labels = scales::percent)

ggsave('img-older/article-revisions-by-month-normalized-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```
So which are the articles that had many revisions in a single month:
```{r}
popular.month.articles <- unique(percents.of.high.revisions$article_id[which(percents.of.high.revisions$percent > .15)])
popular.articles <- percents.of.high.revisions[which(percents.of.high.revisions$article_id %in% popular.month.articles),]
library(directlabels)
# USE THIS - pulled out the three highest articles. add titles to legend remove geom_dl
ggplot(data = popular.articles, aes(x=as.yearmon(date), y = count, colour = total)) + geom_line(aes(group = article_id)) + geom_dl(aes(label=article_id), method = "top.points")


head(revisions_processed)


popular.articles$article_id[popular.articles$article_id == 25431] <- "Russian language"
popular.articles$article_id[popular.articles$article_id == 60341] <- "Richmond, California"
popular.articles$article_id[popular.articles$article_id == 61322] <- "Alcibiades"


high.revisions.per.month.articles <- ggplot(data = popular.articles, aes(x=as.yearmon(date), y = count, colour = as.factor(article_id))) + 
geom_line(aes(group = article_id)) +
labs(title = "Articles that Have High Revisions Within A Single Month", colour = "Article ID") + 
xlab("Year-Month") + 
ylab("Number of Revisions") +
theme(plot.title = element_text(size = rel(1.3)), axis.ticks.length = unit(.25, "cm"))

high.revisions.per.month.articles

ggsave("img/high-revisions-per-month-articles.png", high.revisions.per.month.articles,width = 10, height = 6)

```
25431 = Russian language
60341 = Richmond, California
61322 = Alcibiades

Let's get finer granularity in the dates
```{r}
highest.collapsed.by.day <- revisions_processed[which(revisions_processed$article_id %in% popular.month.articles),] %>%
  group_by(article_id, date) %>%
  summarise(count = n())
arrange(highest.collapsed.by.day, desc(count))


highest.collapsed.by.day$article_id[highest.collapsed.by.day$article_id == 25431] <- "Russian language"
highest.collapsed.by.day$article_id[highest.collapsed.by.day$article_id == 60341] <- "Richmond, California"
highest.collapsed.by.day$article_id[highest.collapsed.by.day$article_id == 61322] <- "Alcibiades"

library(zoo)
high.revisions.per.day.articles <- ggplot(data = highest.collapsed.by.day, aes(x=as.Date(date), y = count, color = as.factor(article_id), alpha = 0.2)) + geom_line() + geom_point(size=0.6) +
  labs(title = "Articles that Have High Revisions Within A Single Day", colour = "Article ID") + 
  xlab("Year-Day") + 
  ylab("Number of Revisions") +
  scale_alpha(guide = 'none') +
  theme(plot.title = element_text(size = rel(1.3)), axis.ticks.length = unit(.25, "cm"))

high.revisions.per.day.articles

ggsave("img/high-revisions-per-day-articles.png", high.revisions.per.day.articles,width = 10, height = 6)

```
On Jan 13, 2007 "Alcibiades" was the wikipedia featured article.
# USE THIS - add screen shot of google search
Many of the edits of "Alcibiades" were done by one author Yannismarou (went on to become an administrator in 2007). Writes tips for how to make a featured article.

Can't tie Russian language to any news and the history for the article doesn't go back as far as this date.

Author of many of the Richmond, CA edits "may need to be blocked due to abusive use of multiple accounts." TROLL? sock puppetry

# Back to all articles
For now, let's normalize by total number of revisions to get percentages.
```{r}
percents <- collapsed %>%
  group_by(article_id) %>%
  mutate(percent = count/sum(count))

library(zoo)
ggplot(data = percents, aes(x=as.yearmon(date), y = percent, colour = article_id)) + geom_line(aes(group = article_id)) + geom_point() 
```
Plot this with first revision to get plot to prove our point about article ids and article age.

In order to align the data to the left, we need to convert the dates to time since first revision. 
```{r}
# this won't work if the data isn't sorted by date
# date of first revision for each article id
t.first <- percents[!duplicated(percents$article_id),]
arrange(t.first, desc(date))
#t.first.before2003 <- subset(t.first, as.yearmon(date) < as.yearmon("2003-01"))
#arrange(t.first.before2003, desc(date))
```

Convert records to time since first revision
```{r}
aligned_revisions <- percents
aligned_revisions$first <- t.first$date[match(aligned_revisions$article_id, t.first$article_id)]
aligned_revisions$time.since.creation <- (as.yearmon(aligned_revisions$date) - as.yearmon(aligned_revisions$first))*12
aligned_revisions$time.since.creation <- as.integer(round(aligned_revisions$time.since.creation))
library(scales)
ggplot(data = aligned_revisions, aes(x=time.since.creation, y = percent, colour = article_id)) + geom_line(aes(group = article_id)) + scale_y_continuous(labels = scales::percent) + geom_point()

ggsave('img-older/article-revisions-since-creation-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```

Okay so there might be some trends that are obfuscated because we do not have 0% for months where there are no edits.
```{r}
library(data.table)
all_months <- as.data.frame(dcast(setDT(aligned_revisions), article_id ~ time.since.creation, value.var='percent'))
all_months[is.na(all_months)] <- 0
all_months

library(reshape2)
library(ggvis)

df1 <- melt(all_months, "article_id")
df1$variable <- as.integer(df1$variable)

ggplot(data = df1, aes(x=variable, y = value, colour = article_id)) + geom_line(aes(group = article_id)) + scale_y_continuous(labels = scales::percent) + geom_point()

ggsave('img-older/article-revisions-by-month-since-creation-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```
Note* we now have 0 in for articles that couldn't have existed that long. So we need to trim the end off.
And we need to recalculate percents to be windows of 5 years. So percent of the revisions that occur in the first five years.

```{r}
filtered_revisions_counts <- collapsed
arrange(filtered_revisions_counts, article_id)
ggplot(data = filtered_revisions_counts, aes(x=as.yearmon(date), y = count, colour = article_id)) + geom_line(aes(group = article_id)) + geom_vline(xintercept = as.yearmon("2003-01"), colour = "red") + scale_color_gradient2(midpoint = 7000000)

ggsave('img-older/article-revisions-filtered-5years-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```

Okay. Now we want need to convert date to months since creations (so we can cap off the first 5 years).
Convert records to time since first revision
```{r}
aligned_revisions_counts <- filtered_revisions_counts
aligned_revisions_counts$first <- t.first$date[match(aligned_revisions_counts$article_id, t.first$article_id)]
aligned_revisions_counts$time.since.creation <- round((as.yearmon(aligned_revisions_counts$date) - as.yearmon(aligned_revisions_counts$first))*12)

library(scales)
ggplot(data = aligned_revisions_counts, aes(x=time.since.creation/12, y = count, colour = article_id)) + geom_line(aes(group = article_id)) + geom_point() + xlab("Years since First Revision")

ggsave('img-older/article-revisions-by-month-since-first-revision-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```
This is really interesting that smaller article_ids (older articles?) were heavily edited around 4-6 years after first creation.
Okay now we need to convert to wide format. Age/article_id aside, there appears to be an upward trend in the number of revisions/month with article age.

```{r}
library(data.table)
aligned.drop.first <- subset(aligned_revisions_counts, select = -c(date,first))
all_months_counts1 <- as.data.frame(dcast(setDT(aligned.drop.first), article_id ~ time.since.creation, value.var='count'))
all_months_counts1[is.na(all_months_counts1)] <- 0

all_months_counts <- as.data.frame(dcast(setDT(aligned.drop.first), article_id ~ time.since.creation, value.var='count'))
all_months_counts[is.na(all_months_counts)] <- 0
all_months_counts$first <- aligned_revisions_counts$first[match(all_months_counts$article_id, aligned_revisions_counts$article_id)]
# reorganize columns
all_months_counts <- all_months_counts %>%
  select(article_id, first, everything())
library(reshape2)
library(ggvis)

# if having issues in future, I adjusted what df1_counts looks like. used to be made with counts not counts1
df1_counts <- reshape2::melt(all_months_counts1, "article_id")
df1_counts$variable <- as.integer(df1_counts$variable)

ggplot(data = df1_counts, aes(x=variable, y = value, colour = article_id)) + geom_line(aes(group = article_id))

ggsave('img-older/article-revisions-by-month-melt-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```

Okay. So since the cut-off date was 2003-01, then the maximum amount of time for revisions is 5 years. Thus we should cut off all the data after 60 months since first revision. Then convert the values to percentages of all revisions.
```{r}

data_5yrs <- all_months_counts[,0:63]
data_5yrs_norm <- data_5yrs
data_5yrs_norm$totalrevisions <- rowSums(data_5yrs[,3:63])
data_5yrs_norm[,3:63] <- data_5yrs[,3:63]/data_5yrs_norm$totalrevisions
df1_5yrs <- melt(data_5yrs_norm, c("article_id", "first", "totalrevisions"))
df1_5yrs$variable <- as.integer(df1_5yrs$variable)

ggplot(data = df1_5yrs, aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=totalrevisions), size = 0.4) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision")


ggsave('img-older/article-revisions-60months-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```
## color by first revision date.
```{r}
ggplot(data = df1_5yrs, aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=first), size = 0.4) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision")

ggsave('img-older/color-by-first-revision-date-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```
Clearly, we need to bin the first creation maybe into quarters?
```{r}
data_5yrs_norm$quarter <- lubridate::quarter(as.yearmon(data_5yrs_norm$first), with_year=TRUE)

df1_5yrs <- melt(data_5yrs_norm, c("article_id", "totalrevisions", "quarter", "first"))
df1_5yrs$variable <- as.integer(df1_5yrs$variable)
df1_5yrs$quarter <- as.factor(df1_5yrs$quarter)

colorsusedquarters <- scales::hue_pal(direction = -1)(length(levels(df1_5yrs$quarter)))
names(colorsusedquarters) <- levels(df1_5yrs$quarter)
group.colors <- c("2001.1" = colorsusedquarters[1], "2001.2" = colorsusedquarters[2], "2001.3" = colorsusedquarters[3], "2001.4" = colorsusedquarters[4], "2002.1" = colorsusedquarters[5],
                  "2001.2" = colorsusedquarters[6], "2001.3" = colorsusedquarters[7], "2001.4" = colorsusedquarters[8])

ggplot(data = df1_5yrs, aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=as.factor(quarter), alpha = 0.2), size = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + scale_color_hue(direction = -1) + facet_grid(~as.factor(quarter)) +  theme(legend.position="none")

ggsave('img-older/article-revisions-60months-facet-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```

```{r}
# USE THIS
percent.revision.since.created <- ggplot(data = df1_5yrs, aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=quarter, alpha = 0.6), size = 0.2) + scale_y_continuous(labels = scales::percent) + 
  ylab("Percent of Article Revisions") + 
  xlab("Months since First Revision") + 
  scale_color_hue(direction = -1) + 
  scale_colour_manual(name = "Quarter", values = colorsusedquarters) + 
  labs(title = "Percent of Articles by Month Since Created", color = "Fiscal Quarter of First Revision") + 
  scale_alpha(guide = 'none')+
  theme(plot.title = element_text(size = rel(1.3)), axis.ticks.length = unit(.25, "cm"))

percent.revision.since.created

ggsave("img/percent-revision-since-created.png", percent.revision.since.created,width = 10, height = 6)

# USE THIS
percent.revision.since.created.no.200204 <- ggplot(data = df1_5yrs[which(df1_5yrs$quarter != "2002.4"),], aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=quarter, alpha = 0.6), size = 0.2) + scale_y_continuous(labels = scales::percent) + 
  ylab("Percent of Article Revisions") + 
  xlab("Months since First Revision") + 
  scale_colour_manual(name = "Quarter", values = colorsusedquarters) + 
  labs(title = "Percent of Articles by Month Since Created (Without 2002.4)", color = "Fiscal Quarter of First Revision") + 
  scale_alpha(guide = 'none')+
  theme(plot.title = element_text(size = rel(1.3)), axis.ticks.length = unit(.25, "cm"))

percent.revision.since.created.no.200204
ggsave("img/percent-revision-since-created-no-200204.png", percent.revision.since.created.no.200204,width = 10, height = 6)

```

```{r}
ggplot(data = df1_5yrs[which(!df1_5yrs$quarter %in% c("2002.4","2002.3")),], aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=quarter, alpha = 0.2), size = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + scale_colour_manual(name = "quarter", values = colorsusedquarters) + labs(color = "Fiscal Quarter of First Revision") + scale_alpha(guide = 'none')

ggsave('img-older/article-revisions-quarters1-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)

ggplot(data = df1_5yrs[which(!df1_5yrs$quarter %in% c("2002.4","2002.3", "2002.2")),], aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=quarter, alpha = 0.2), size = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + scale_colour_manual(name = "quarter", values = colorsusedquarters) + labs(color = "Fiscal Quarter of First Revision") + scale_alpha(guide = 'none')

ggsave('img-older/article-revisions-quarters2-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)



ggplot(data = df1_5yrs[which(!df1_5yrs$quarter %in% c("2002.4","2002.3", "2002.2", "2002.1")),], aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=quarter, alpha = 0.2), size = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + scale_colour_manual(name = "quarter", values = colorsusedquarters) + labs(color = "Fiscal Quarter of First Revision") + scale_alpha(guide = 'none')

ggsave('img-older/article-revisions-quarters3-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)


ggplot(data = df1_5yrs[which(!df1_5yrs$quarter %in% c("2002.4","2002.3", "2002.2", "2002.1", "2001.4")),], aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=quarter, alpha = 0.2), size = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + scale_colour_manual(name = "quarter", values = colorsusedquarters) + labs(color = "Fiscal Quarter of First Revision") + scale_alpha(guide = 'none')

ggsave('img-older/article-revisions-quarters4-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)


ggplot(data = df1_5yrs[which(!df1_5yrs$quarter %in% c("2002.4","2002.3", "2002.2", "2002.1", "2001.4", "2001.3")),], aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=quarter, alpha = 0.2), size = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + scale_colour_manual(name = "quarter", values = colorsusedquarters) + labs(color = "Fiscal Quarter of First Revision") + scale_alpha(guide = 'none')

ggsave('img-older/article-revisions-quarters5-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)

```

Let's explore articles from the last quarter
```{r}
ggplot(data = df1_5yrs[which(df1_5yrs$quarter == "2002.4"),], aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=quarter, alpha = 0.2), size = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + scale_colour_manual(name = "quarter", values = colorsusedquarters) + labs(color = "Fiscal Quarter of First Revision") + scale_alpha(guide = 'none')

ggsave('img-older/last-quarter-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)

# USE THIS
percent.revision.since.created.last.quarter <- ggplot(data = df1_5yrs[which(df1_5yrs$quarter == "2002.4"),], aes(x=variable, y = value)) + 
  geom_line(aes(group = article_id, color=first, alpha = 0.2), size = 0.2) + scale_y_continuous(labels = scales::percent) + 
  ylab("Percent of Article Revisions") + 
  xlab("Months since First Revision") + 
  scale_alpha(guide = 'none')+
  labs(title = "Percent of Articles by Month Since Created (Last Quarter)", color = "Quarter") + 
  theme(plot.title = element_text(size = rel(1.3)), axis.ticks.length = unit(.25, "cm"))

percent.revision.since.created.last.quarter
ggsave("img/percent-revision-since-created-last-quarter.png", percent.revision.since.created.last.quarter,width = 10, height = 6)


ggplot(data = df1_5yrs[which(df1_5yrs$first %in% c("2002-09", "2002-10", "2002-11", "2002-12")),], aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=first, alpha = 0.2), size = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + labs(color = "Month of First Revision") + scale_alpha(guide = 'none') + facet_grid(~as.factor(first))

ggsave('img-older/last-quarter-2002-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)

```
I want to know how many articles are produced per month, and per quarter
```{r}
article_count_by_month <- df1_5yrs %>%
  dplyr::group_by(first) %>%
  dplyr::summarise(count = n())

ggplot(data = article_count_by_month, aes(x=as.yearmon(first), y = count)) + geom_line(size = 0.5) + ylab("Number of Articles First Revised") + xlab("Date of First Revision") + scale_x_yearmon(format = "%b %Y", n=24, labels = function(x) lapply(strwrap(x, width = 5, simplify = FALSE), paste, collapse="\n")) 
ggsave('img-older/articles-per-month-per-quarter-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)

# USE THIS but fix x-axis
first.article.revisions.by.year.month <- ggplot(data = article_count_by_month, aes(x=as.integer(format(as.yearmon(first), "%m")), y = count)) + 
  geom_line(size = 0.5) + 
  ylab("Number of Articles First Revised") + 
  xlab("Date of First Revision") + 
  facet_grid(. ~ format(as.yearmon(first), "%Y")) + 
  scale_x_discrete(breaks=c(1:12))+
  labs(title = "Number of First Article Revisions by Month", color = "Quarter") + 
  theme(plot.title = element_text(size = rel(1.3)), axis.ticks.length = unit(.25, "cm"))

first.article.revisions.by.year.month
ggsave("img/first-article-revisions-by-year-month.png", first.article.revisions.by.year.month,width = 10, height = 6)



article_count_by_quarter <- df1_5yrs %>%
  group_by(quarter) %>%
  dplyr::summarise(count = n())


ggplot(data = article_count_by_quarter, aes(x=quarter, y = count)) + geom_point(size = 0.5) + ylab("Number of Articles First Revised") + xlab("Quarter of First Revision")
ggsave('img-older/article-count-by-quarter-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```

## Coloring by number of revisions
I want to discretize the number of total revisions
```{r}
data_5yrs_norm$bins <- cut(data_5yrs_norm$totalrevisions, breaks=c(0,2,10,25,100, 500, 20000), labels=c("1-2", "3-10", "10-25", "25-100", "100-500", "500-"))

df1_5yrs <- melt(data_5yrs_norm, c("article_id", "totalrevisions", "bins", "quarter", "first"))
df1_5yrs$variable <- as.integer(df1_5yrs$variable)

# USE THIS
ggplot(data = df1_5yrs, aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=bins, alpha = 0.2), size = 0.5) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + scale_color_hue(direction = -1) + facet_grid(~bins) +  theme(legend.position="none") + scale_alpha(guide = 'none')


ggplot(data = df1_5yrs, aes(x=variable, y = value)) + 
  geom_line(aes(group = article_id, 
                color=bins, 
                alpha = 0.2), 
            size = 0.5) + 
  scale_y_continuous(labels = scales::percent) + 
  ylab("Percent of Article Revisions") + 
  xlab("Months Since First Revision") + 
  scale_color_hue(direction = -1) + 
  facet_grid(~bins) +  
  theme(legend.position="none") + 
  scale_alpha(guide = 'none') + 
  ggtitle("Articles By Total Revisions")

ggsave("img/articles-by-total-revisions-facet.png", 
       plot = last_plot(),
       width = 10,
       height = 6)

```

```{r}
ggplot(data = df1_5yrs, aes(x=variable, y = value)) + 
  geom_line(aes(group = article_id, color=bins, alpha = 0.8), size = 0.8) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + 
  xlab("Months since First Revision") + scale_color_hue(direction = -1) + labs(color = "Total Article Revisions") 
# + scale_alpha(guide = "none")

ggsave('img-older/monts-since-first-revision-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)

```

```{r}

# USE THIS
ggplot(data = df1_5yrs, aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=bins, alpha = 0.8), size = 0.8) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + scale_color_hue(direction = -1) + labs(color = "Total Article Revisions")

# USE THIS
ggplot(data = df1_5yrs, aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=bins, alpha = 0.2), size = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + scale_color_hue(direction = -1) + labs(color = "Total Article Revisions")
```


```{r}
factorlevels <- levels(df1_5yrs$bins)
colorsused <- scales::hue_pal(direction = -1)(length(factorlevels))
counter <- 1
for (f in factorlevels){
  print(ggplot(data = df1_5yrs[df1_5yrs$bins == f,], aes(x=variable, y = value)) + geom_line(aes(group = article_id), color=colorsused[counter], size = 0.6, alpha = 0.5) + scale_y_continuous(labels = scales::percent, limits = c(0,1)) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + facet_grid(~bins) + theme(legend.position="none") )
  
  ggsave(paste0('img-older/', 'months-since-first-revision-facet-', f, 'sample2.png'), 
       plot = last_plot(),
       width = 10,
       height = 6)
  
  print(ggplot(data = df1_5yrs[df1_5yrs$bins == f,], aes(x=variable, y = value)) + geom_line(aes(group = article_id), color=colorsused[counter], size = 0.6, alpha = 0.5) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision") + facet_grid(~bins) + theme(legend.position="none") )
  
    ggsave(paste0('img-older/', 'months-since-first-revision-facet-scaled-', f, 'sample2.png'), 
       plot = last_plot(),
       width = 10,
       height = 6)
  
  
  
  counter <- counter +1
}
```

Articles with few revisions tend to be revised close to their creation, and articles that are heavily revised have most of their revisions further away from their creation date.
Strong peak around 26 months for 10-25 revisions and can still see it for articles with 25-100 revisions.

```{r}
articles.10.2002 <- aligned_revisions[which(first == "2002-10")] 
articleids.10.2002 <- unique(articles.10.2002$article_id)

# USE THIS - screenshot
(article.names.10.2002 <- unique(revisions_processed$article_title[which(revisions_processed$article_id %in% articleids.10.2002)]))


# Lydia's google searching identifies Rambot, created by RamMan
```


```{r}

collapsed.by.day <- revisions_processed[which(revisions_processed$article_id %in% articleids.10.2002),] %>%
  group_by(date) %>%
  summarise(count = n(), unique.articles = length(unique(article_id)))
arrange(collapsed.by.day, desc(count))
head(collapsed.by.day)

library(zoo)
# USE THIS - add legend, title
ggplot(data = collapsed.by.day, aes(x=as.Date(date))) + geom_line(aes(y = count), color = "blue") + geom_line(aes(y=unique.articles), color = "lightblue")
# Add Lydia's discovery of KevinBot
```
These are articles that were first revised in October of 2002. Blue is the number of article revisions by day (each point is a single day). We see there are many revisions shortly after, and then again around 2 years later. There are 337 articles in this dataset that were first revised in Oct of 2002. The black is the number of unique articles revised. When black is as high as blue, the revisions for that date are all on unique articles. When black is lower than blue, there were multiple revisions on single articles for that date. So ~105 of the 337 article first revised on Oct 2002 were also edited around a single time ~ 2 yrs later. 

```{r}
arrange(collapsed.by.day, desc(count))

authors.question <- revisions_processed[which(revisions_processed$article_id %in% articleids.10.2002),] %>%
  group_by(article_id) %>%
  dplyr::summarise(count = n(), unique.articles = length(unique(article_id)), proportion = count/unique.articles)

arrange(authors.question, desc(count))
```

## categories

```{r}
categories <- do.call(rbind,strsplit(readLines("data/1000categories.txt"), "\x1e"))
categories <- as.data.frame(categories)
names(categories) <- c("article_id", "category")
cat.unique.counts <- categories %>%
  group_by(category) %>%
  summarize(count = n())
arrange(cat.unique.counts, desc(count))
arrange(categories, desc(article_id))
articles.with.categories <- as.integer(levels(unique(categories$article_id)))
```

These are not going to be very helpful. Wikipedia category hierarchy is complex and circular and it is not easy to find root categories.
We need to pull all article categories and then we can pull all articles in particular high ranking categories like living people vs not living people, technology vs history etc.

# Article Tags
```{r}
tags <- as.data.frame(do.call(rbind,strsplit(readLines("data/all_oldenough_indicators.txt"), "\x1e",fixed=T)), stringsAsFactors = FALSE)
tags$V2 <- as.factor(tags$V2)
wikinames <- levels(tags$V2)
replacement.names <- c("Featured Article", "Good Article", "Journal", "Help Link", "Partially Protected - Autoreview", "Partially Protected - Default", "Spoken")
library(plyr)
tags$V2 <- mapvalues(tags$V2, from = wikinames, to = replacement.names)
names(tags) <- c("article_id", "Indicator")
tags$article_id <- as.integer(tags$article_id)
arrange(tags, article_id)

data.with.indicators <- merge(tags, df1_5yrs, by='article_id', all=TRUE, sort=FALSE)
data.with.indicators <- data.with.indicators[!is.na(data.with.indicators$first),]
arrange(data.with.indicators,article_id,quarter)


# Plot percents by tags
ggplot(data = data.with.indicators, aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=Indicator), size = 0.4, alpha = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision")

ggsave('img-older/percents-by-tags.png', 
       plot = last_plot(),
       width = 10,
       height = 6)


```
```{r}
# let's hide the articles that were first created in Oct 2002
data.with.indicators.drop.oct.2002 <- data.with.indicators[which(data.with.indicators$first != "2002-10"),]

# Plot percents by tags
ggplot(data = data.with.indicators.drop.oct.2002, aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=Indicator), size = 0.4, alpha = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision")

ggsave('img-older/percents-by-tags-without-oct2002.png', 
       plot = last_plot(),
       width = 10,
       height = 6)

ggplot(data = data.with.indicators.drop.oct.2002[which(!is.na(data.with.indicators.drop.oct.2002$Indicator)),], aes(x=variable, y = value)) + geom_line(aes(group = article_id, color=Indicator), size = .5, alpha = 0.2) + scale_y_continuous(labels = scales::percent) + ylab("Percent of Article Revisions") + xlab("Months since First Revision")

ggsave('img-older/percents-by-tags-without-oct2002-without-nas.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```

Nothing really pops out with percentages. Show this with counts instead.
```{r}
data.count.indicators <- merge(tags, collapsed, by="article_id", all = TRUE, sort = FALSE)
data.count.indicators <- data.count.indicators[!is.na(data.count.indicators$date),]
arrange(data.count.indicators,article_id)

# USE THIS
ggplot(data = data.count.indicators, aes(x=as.yearmon(date), y = count, colour = Indicator)) + geom_line(aes(group = article_id), size = .7, alpha = 0.5) + geom_point(size = .6)

ggplot(data = data.count.indicators[which(!is.na(data.count.indicators$Indicator)),], aes(x=as.yearmon(date), y = count, colour = Indicator), size = 0.7, alpha = 0.3) + geom_line(aes(group = article_id), size = .7, alpha = 0.5) + geom_point(size = .6)
```

It's pretty clear that article's with tags are more popular for revisions.

Let's look at which articles have been deleted.
```{r}
deleted.articles <- read.csv("data/badtitles1000sample.txt")
deleted.articles <- deleted.articles[,1]
data.count.indicators$Indicator <- as.character(data.count.indicators$Indicator)
data.count.indicators[which(data.count.indicators$article_id %in% deleted.articles), "Indicator"] <- "Deleted Article IDs"
# need to clean article_id 1073 as a bad article. It was not identified as a bad article during the scraping
data.count.indicators[which(data.count.indicators$article_id == 1073), "Indicator"] <- "Deleted Article IDs"
data.count.indicators$Indicator <- as.factor(data.count.indicators$Indicator)

ggplot(data = data.count.indicators, aes(x=as.yearmon(date), y = count, colour = Indicator)) + geom_line(aes(group = article_id), size = .7, alpha = 0.5) + geom_point(size = .6)

# USE THIS
ggplot(data = data.count.indicators[which(!is.na(data.count.indicators$Indicator)),], aes(x=as.yearmon(date), y = count, colour = Indicator)) + geom_line(aes(group = article_id), size = .8, alpha = 0.6) + geom_point(size = .75)

ggplot(data = data.count.indicators[which(!is.na(data.count.indicators$Indicator) & data.count.indicators$Indicator == "Deleted Article IDs"),], aes(x=as.yearmon(date), y = count, colour = Indicator)) + geom_line(aes(group = article_id), size = .8, alpha = 0.6) + geom_point(size = .75)

ggsave('img-older/article-revisions-by-year-deleted-articleids.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```

# Living people
```{r}
# we are interested in doing this again on the complete old enough articles!!
living.people.article.ids <- unique(as.character(categories[which(categories$category == "Living people"), "article_id"]))

living.people.indicator <- collapsed
living.people.indicator$LivingPerson <- NA
living.people.indicator[which(living.people.indicator$article_id %in% living.people.article.ids), "LivingPerson"] <- "Living People"

library(zoo)

ggplot(data = living.people.indicator, aes(x=as.yearmon(date), y = count, colour = as.factor(LivingPerson), alpha = 0.5)) + geom_line(aes(group = article_id), alpha=0.5, size = 0.4) + geom_point(size = 1.0)
ggsave('img-older/living-people-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)

ggplot(data = living.people.indicator[which(!is.na(living.people.indicator$LivingPerson)),], aes(x=as.yearmon(date), y = count, alpha = 0.5)) + geom_line(aes(group = article_id), alpha=0.5, size = 0.4) + geom_point(size = 0.8)+ geom_dl(aes(label=article_id), method = "top.points")

ggsave('img-older/living-people-top-points-sample2.png', 
       plot = last_plot(),
       width = 10,
       height = 6)
```

Who is that super popular living person?
```{r}
popularperson <- as.integer(unique(living.people.indicator[which(!is.na(living.people.indicator$LivingPerson) & living.people.indicator$count > 100),"article_id"]))
# 162864 is Lauryn Hill https://en.wikipedia.org/?curid=162864
popularpeople <- living.people.indicator %>%
  filter(!is.na(LivingPerson))%>%
  group_by(article_id) %>%
  dplyr::summarize(totalrevisions = sum(count)) %>%
  arrange(desc(totalrevisions))
popularpeople
```

Are articles deleted?
Is there a trend in articles that don't have categories?
```{r}
# show articles that don't have categories
no.categories.articles <- collapsed %>%
  filter(!article_id %in% articles.with.categories) %>%
  group_by(article_id) %>%
  dplyr::summarise(totalrevisions = sum(count))

# how many of these articles were "bad titles"
(mysteriousarticles <- no.categories.articles %>%
  filter(!article_id %in% deleted.articles))

# this produces only the article 1073, but looking through browser shows that this article is a "bad title"
# this was fixed in the above code
```
```{r}
allcategories <- as.data.frame(do.call(rbind,strsplit(readLines("data/Categories_all_oldenough.txt"), "\x1e",fixed=T)), stringsAsFactors = FALSE)
allcategories <- as.data.frame(allcategories)
names(allcategories) <- c("article_id", "category")
all.cat.unique.counts <- allcategories %>%
  group_by(category) %>%
  dplyr::summarize(count = n())
arrange(all.cat.unique.counts, desc(count))
```
```{r}
manually.all.cat.unique.counts <- all.cat.unique.counts
manually.all.cat.unique.counts$manual.category <- manually.all.cat.unique.counts$category
geo.list <- c("Cities", "Townships", "Towns in", "Villages in", "places in", "cities", "towns", "Counties", "metropolitan area", "counties", "Municipalities of", "Member states", "Areas of", "metroplex", "Populated places")
for (g in geo.list){
  manually.all.cat.unique.counts[which(all.cat.unique.counts$category %like% g), "manual.category"] <- "Geography"
}
manually.all.cat.unique.counts[which(all.cat.unique.counts$category %like% "isambiguation pages"), "manual.category"] <- "Disambiguation pages"
manually.all.cat.unique.counts[which(all.cat.unique.counts$category %like% "films"), "manual.category"] <- "Films"
grouped.manually.all.cat.unique.counts <- manually.all.cat.unique.counts %>%
  group_by(manual.category) %>%
  dplyr::summarize(count = sum(count))
arrange(grouped.manually.all.cat.unique.counts, desc(count))

# maybe some article_id have multiple tags with film in them. have to control for that
```

